Bogor/Kiasan foi publicado em:

Bogor/Kiasan: A k-bounded Symbolic Execution for Checking Strong Heap Properties of Open Systems

IEEE Xplore: "((Kiasan/Bogor) OR Bogor/Kiasan)"
http://ieeexplore.ieee.org

18 resultados

"A Scalable Distributed Concolic Testing Approach: An Empirical Evaluation," 2012 IEEE Fifth International Conference on Software Testing, Verification and Validation, Montreal, QC, 2012, pp. 340-349.
"Formal Software Analysis Emerging Trends in Software Model Checking," Future of Software Engineering, 2007. FOSE '07, Minneapolis, MN, 2007, pp. 120-136.
"On the Techniques We Create, the Tools We Build, and Their Misalignments: A Study of KLEE," 2016 IEEE/ACM 38th International Conference on Software Engineering (ICSE), Austin, TX, 2016, pp. 132-143.
"MPISE: Symbolic Execution of MPI Programs," 2015 IEEE 16th International Symposium on High Assurance Systems Engineering, Daytona Beach Shores, FL, 2015, pp. 181-188.
"Symbolic execution for software testing in practice: preliminary assessment," 2011 33rd International Conference on Software Engineering (ICSE), Honolulu, HI, 2011, pp. 1066-1071.
"Finding errors from reverse-engineered equality models using a constraint solver," 2012 28th IEEE International Conference on Software Maintenance (ICSM), Trento, 2012, pp. 77-86.
"Verification-Based Test Case Generation for Full Feasible Branch Coverage," 2008 Sixth IEEE International Conference on Software Engineering and Formal Methods, Cape Town, 2008, pp. 159-168.
"Path coverage testing in the cloud," 2012 International Conference on Communications and Information Technology (ICCIT), Hammamet, 2012, pp. 118-123.
"Bogor: A Flexible Framework for Creating Software Model Checkers," Testing: Academic & Industrial Conference - Practice And Research Techniques (TAIC PART'06), Windsor, 2006, pp. 3-22.
"Generating unit tests using static analysis and contracts," 2013 Tools & Methods of Program Analysis, Kostroma, 2013, pp. 83-88.
"Kiasan/KUnit: Automatic Test Case Generation and Analysis Feedback for Open Object-oriented Systems," Testing: Academic and Industrial Conference Practice and Research Techniques - MUTATION (TAICPART-MUTATION 2007), Windsor, 2007, pp. 3-12.
"Environment generation for validating event-driven software using model checking," in IET Software, vol. 4, no. 3, pp. 194-209, June 2010.
"Towards A Case-Optimal Symbolic Execution Algorithm for Analyzing Strong Properties of Object-Oriented Programs," Fifth IEEE International Conference on Software Engineering and Formal Methods (SEFM 2007), London, 2007, pp. 273-282.
"Bogor/Kiasan: A k-bounded Symbolic Execution for Checking Strong Heap Properties of Open Systems," 21st IEEE/ACM International Conference on Automated Software Engineering (ASE'06), Tokyo, 2006, pp. 157-166.
"Dynamic Data Flow Testing of Object Oriented Systems," 2015 IEEE/ACM 37th IEEE International Conference on Software Engineering, Florence, 2015, pp. 947-958.
"Heap cloning: Enabling dynamic symbolic execution of java programs," 2011 26th IEEE/ACM International Conference on Automated Software Engineering (ASE 2011), Lawrence, KS, 2011, pp. 33-42.
"Domain-specific Model Checking Using The Bogor Framework," 21st IEEE/ACM International Conference on Automated Software Engineering (ASE'06), Tokyo, 2006, pp. 369-370.
"Test generation through programming in UDITA," 2010 ACM/IEEE 32nd International Conference on Software Engineering, Cape Town, 2010, pp. 225-234.

ACM DL: content.ftsec:("Bogor/Kiasan")
http://dl.acm.org

19 resultados

A Publish-subscribe Architecture and Component-based Programming Model for Medical Device Interoperability
Combining Symbolic Execution and Search-based Testing for Programs with Complex Heap Inputs
Combining Unit-level Symbolic Execution and System-level Concrete Execution for Testing Nasa Software
DSD-Crasher: A Hybrid Analysis Tool for Bug Finding
Dynamic Data Flow Testing of Object Oriented Systems
Efficient Modular Glass Box Software Model Checking
Enhancing Symbolic Execution with Built-in Term Rewriting and Constrained Lazy Initialization
Heap Cloning: Enabling Dynamic Symbolic Execution of Java Programs
JBSE: A Symbolic Executor for Java Programs with Complex Heap Inputs
jStar: Towards Practical Verification for Java
On the Techniques We Create, the Tools We Build, and Their Misalignments: A Study of KLEE
Preliminary Design of a Unified JML Representation and Software Infrastructure
Sireum/Topi LDP: A Lightweight Semi-decision Procedure for Optimizing Symbolic Execution-based Analyses
Symbolic Execution for Software Testing in Practice: Preliminary Assessment
Symbolic Execution of Programs with Heap Inputs
Symbolic PathFinder: Symbolic Execution of Java Bytecode
Test Generation Through Programming in UDITA
Towards a Lazier Symbolic Pathfinder
Towards Verifiable Deeply Embedded Systems
